### 2016-06-22 appendix.tex
Revised section 5
fff

\subsection{Proof of Theorem~\ref{THM:SPM_FCC}}
\begin{proof}
We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
\end{proof}

>>>>

\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT}}
\begin{proof}
For soundness, let $P$ be a pattern enumerated by SPARE, then $\forall o_1, o_2 \in P.O$ they belongs to the same star. As the enumerate algorithm only reduce the time sequences, $P.T \subset e(o_1,o_2)$. This indicates that, $\forall t \in P.T$, $t\in e(o_1,o_2)$. By the definition of star, $C_t(o_1) = C_t(o_2)$. Since $P.T$ conforms to $K,L,G$,  by the definition of GCMP, $P.T$ is a true pattern.
For completeness, let $P$ is a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} with $Sr_s$. 
First, based on the definition of star partition, every object in $P.O$ appears in $Sr_s$. Note that $P.T$ conforms to $K,L,G$, then $\forall O' \subseteq O$, the time sequence of $O'$ is a super set of a decomposable sequence. This indicates that any $O'$ would not be eliminated by any $\mathtt{sim}$ operations in Algorithm~\ref{algo:apriori_mining}.  Next, we prove in iterations $(1,\ldots,P.|O|-2)$, $P.O \subset U_i$, where $U_i$ is the forward closure. We prove by induction. When $i$ = 2, it obviously holds. If $P.O \subset U_i$ at iteration $i$, then any subset of $P.O$ with size $i+2$ are in the candidate set. In iteration $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$). This suggests that no subsets are removed by Line~\ref{code:output1}. Then, $P.O \subset U_{i+1}$ holds.  In summary, $P.O$ does not pruned by simplification and monotonicity and forward closure, therefore $P$ can be returned by SPARE.
%Next, observe that at each iteration $i$, candidates with size $i+2$ are generated. Then, $P.O$'s subset with size $i+2$ are always included in the candidate set at iteration $i$. This indicates that $O' \subset U$, thus any $O'$  would not be pruned by forward closure checking. Since none of the pruning operations removed $O'$, $P$ can be returned by SPARE.
%
%\begin{theorem}[Forward Closure Checking]
%\label{THM:SPM_FCC}
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
%if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
%and directly output $FC_i$.
%\end{theorem}

%
%If $P$ is a valid pattern in original trajectories, 
%let $s$ be the object with smallest ID in $P.O$. 
%Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
%It follows that all object $o \in P.O$ are in $Sr_s$. 
%Furthermore, every timestamp in $P.T$ is included
%in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$. This ensures the \emph{completeness}. For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$. This ensure the \emph{soundness}.
\end{proof}

%\subsection{Proof of Theorem~\ref{THM:SPM_FCC}}
%\begin{proof}
%We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
%let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
%(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
%then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
%It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
%\end{proof}

### 2016-06-22 sec5_spm.tex
Revised section 5
fff

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension 
and results in groups of snapshots in each partition. ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

\begin{theorem}\label{THM:SPM_TM}
Given a candidate pattern $P=\{O:T\}$, if $\mathtt{sim}(P.T)=\emptyset$, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
\end{theorem}

@@

\subsubsection{Apriori Enumeration}
We then design the Apriori enumeration method to
systematically discover all valid patterns in a star.
During the enumeration, we refer a candidate pattern
$P$ as a $R$-candidate if $|P.O|=R$. The enumeration
method discover patterns in ``bottom-up'' order:
in iteration $i$,  all $(i+1)$-candidates grows
to $(i+2)$-candidates. Enumeration ends if no
further candidates can be generated.

The process of enumeration is shown 
in Algorithm~\ref{algo:apriori_mining}. As a start, 
each edge is treated as a $2$-candidate pattern, with the 
inverted list as the time sequence. These $2$-candidates
are kept in $\mathbf{G}$ as the ground set. During the algorithm,
we maintain a set of candidates $\mathbf{C}$. $\mathbf{C}$
is initialized as $\mathbf{G}$.

As a start, each edge is treated as

@@

To describe the algorithm, we call a candidate pattern $R$-pattern 
if the size of its object set is $R$.  Therefore, each edge
in the star is effectively a $2$-pattern. The intuition of Apriori mining
is the observation that $(R+1)$-patterns can be generated
from $R$-patterns and $2$ patterns. Thus, we may iteratively 
enumerate pattern candidates with all possible sizes.
In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
each $R$-pattern contains the object $s$, thus the join only 
grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. 
The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$\mathbf{C} \gets \{\}$, $\mathbf{G} \gets \{\}$, $\mathbf{OT} \gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State {$T' \gets \mathtt{sim}(e(s,t))$}
%\State{ $\mathtt{sim}(e(s,t)) $} 
\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}
\EndFor
\State {$\mathbf{C} \gets \mathbf{G}$}
\While{$\mathbf{C} \neq \emptyset$}
		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
		\ForAll{$(c,g)\in \mathbf{C}$}
			\ForAll {$g \in \mathbf{G}$ }
				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$}
				\State {$\mathbf{N}.add(c')$, unless $c'.T \neq \emptyset$}
			\EndFor
			\State $\mathbf{OT}.\mathtt{add}(c)$, if $c$ is not extended.
		\EndFor	
		\State $U \gets $ union of $n_i \in \mathbf{N}$
		\ForAll{$n \in \mathbf{N}$}
			\State $U.O \gets$,  $U.T \gets U.T \cap n.T$
		\EndFor
		\If{$U$ is valid}
			\State $\mathbf{Output}.\mathbf{add}(U)$
			\State break;
		\EndIf
		\State {$\mathbf{C} \gets \mathbf{N}$}
		\State {Lv $\gets$ Lv $\oplus $ Ground} \Comment{ Simplification}
		\State {Remove false patterns in Lv}
		\Comment{Monotonicity}
		\If{union of Lv is a valid pattern}\Comment{Forward Closure}
			\State{output.add(Lv)} 
			\State{break}
		\EndIf
\EndWhile
\State output.addAll($Lv$)
\State \Return output
\end{algorithmic}
\end{algorithm}

An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
higher level candidates are generated by joining lower level candidates. When no more candidates 
can be generated, the algorithm stops by outputting the valid patterns.
%
%It is notable that, in star partition, original data is 
%replicated at most $O(|\mathbb{O}|)$ times.
%In later sections, we will describe several 
%more optimization techniques to further reduce the amount of replicated data.

@@

@@

It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
reduces, thus the terminating power of $FC$ would be stronger. We give hybrid example of the three
optimization as follows:
%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
%all candidates. Then, the following \emph{forward closure checking} rule can be used:
%
%\begin{theorem}[Forward Closure Checking Rule]
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
%$FC_i$ forms a valid GCMP .
%\end{theorem}

\subsection{Correctness of SPARE}
We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship. In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers. Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created. Then the Apriori algorithm enumerate the true patterns from the candidate patterns. Meanwhile, the \emph{simplification}, \emph{monotonicity pruning} and \emph{forward closure checking} are applied to boost the enumeration process.
\eat{ ADD THE DETAILS WHEN THE REDUCER RECEIVE THE STAR PARTITIONS. HOW THEY DERIVE THE FINAL RESULT PATTERNS.}

@@

In the following, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
If $P$ is a valid pattern in original trajectories, 
let $s$ be the object with smallest ID in $P.O$. 
Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
It follows that all object $o \in P.O$ are in $Sr_s$. 
Furthermore, every timestamp in $P.T$ is included
in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$. This ensures the \emph{completeness}. For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$. This ensure the \emph{soundness}.
\end{proof}.

@@

This lemma verifies the superiority of the SPARE framework over the TRPM framework.

>>>>

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks. First, the replication relies on $\eta$ which could be large. Second, the same valid pattern may be discovered from different partitions which results in redundant work.
%and results in groups of snapshots in each partition.
% ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

\begin{theorem}\label{THM:SPARE_MONO}
Given a candidate pattern $P=\{O:T\}$, if $\mathtt{sim}(P.T)=\emptyset$, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
\end{theorem}

@@

\subsubsection{Apriori Enumeration}
We then design the Apriori enumeration method to
systematically discover all valid patterns in a star.
%During the enumeration, we refer a candidate pattern
%$P$ as a $R$-candidate if $|P.O|=R$.
The enumeration method discover patterns iteratively using ``bottom-up'' order:
candidates with smaller objects set grow one object per iteration.
%
%in iteration $i$,  all $(i+1)$-candidates grows
%to $(i+2)$-candidates.
%
Enumeration ends if no
further candidates can be generated.

 Due the \emph{monotoniciy} proved in Theorem~\label{THM:SPARE_MONO}, we are able to use the \emph{monotonicity pruning} and \emph{forward closure checking} techniques to boost the enumeration process. We show the detail of the process
in Algorithm~\ref{algo:apriori_mining}. As a start, 
each input edge is treated as a candidate pattern, with the 
inverted list as the time sequence. These candidates
are kept in $\mathbf{G}$ as the ground set (Lines~\ref{code:init-start}-\ref{code:init-end}). During the initialization of $\mathbf{G}$, the inverted list are simplified (Line~\ref{code:simp1}) and unqualified edges are pruned (Line~\ref{code:init-prune}). Throughout the algorithm, we maintain a set of candidates denoted as $\mathbf{C}$ which is initialized to be the ground set $\mathbf{G}$ (Line~\ref{code:init-C}).

In each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}),  the members in candidate set are joined with the members in ground set to generate new candidates (Lines~\ref{code:join-start}-\ref{code:join-ends}). The join of two candidate $c$ and $g$ creates a 
new candidate, whose objects are the union of $c.O$ and$g.O$ and the time sequence is the intersection of $c.T$ and $g.T$ (Line~\ref{code:join}). During the join, we use \emph{sequence simplification} to detect unqualified candidates. By \emph{monotonicity}, these candidates are safely excluded from the future iterations~(Line~\ref{code:mono-pruning}). If a candidate is not able to be extended by any ground set, we directly output it (Line~\ref{code:output1}).

After the join process has finished, we start a \emph{forward closure} check (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-ends}). The forward closure checking is to test whether the union of all the candidates in $\mathbf{C}$ form a pattern. If the check succeeds, we output such union and stop the iteration~(Lines~\ref{code:fc-checking}).

\eat{
to union all the candidates in the current candidate set, and quickly check whether the

@@

To describe the algorithm, we call a candidate pattern $R$-pattern 
if the size of its object set is $R$.  Therefore, each edge
in the star is effectively a $2$-pattern. The intuition of Apriori mining
is the observation that $(R+1)$-patterns can be generated
from $R$-patterns and $2$ patterns. Thus, we may iteratively 
enumerate pattern candidates with all possible sizes.
In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
each $R$-pattern contains the object $s$, thus the join only 
grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. 
The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
}

\begin{algorithm}
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$\mathbf{C} \gets \{\}$, $\mathbf{G} \gets \{\}$, $\mathbf{OT} \gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$} \label{code:init-start}
\State {$T' \gets \mathtt{sim}(e(s,t))$} \label{code:simp1}
\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}\label{code:init-prune}
\EndFor\label{code:init-end}
\State {$\mathbf{C} \gets \mathbf{G}$}\label{code:init-C}
\While{$\mathbf{C} \neq \emptyset$} \label{code:level-start}
		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
		\ForAll{$(c,g)\in \mathbf{C}$} \label{code:join-start}
			\ForAll {$g \in \mathbf{G}$}		
				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$} \label{code:join}
				\State {$\mathbf{N}$.add$(c')$, unless $c'.T \neq \emptyset$} \label{code:mono-pruning}
			\EndFor
			\State $\mathbf{OT}$.add$(c)$, if $c$ is not extended.\label{code:output1}
		\EndFor	\label{code:join-ends}
		\State $U \gets $ union of $n_i \in \mathbf{N}$	\label{code:fc-checking-start}
		\If {$U$ is a valid pattern}
			\State $\mathbf{Output}.\mathbf{add}(U)$ \label{code:fc-checking}
			\State break;
		\EndIf \label{code:fc-checking-ends}
		\State {$\mathbf{C} \gets \mathbf{N}$}
\EndWhile\label{code:level-ends}
\State $\mathbf{OT}$.addAll$(\mathbf{C})$
\State \Return $\mathbf{OT}$
\end{algorithmic}
\end{algorithm}

%An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
%As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
%higher level candidates are generated by joining lower level candidates. When no more candidates 
%can be generated, the algorithm stops by outputting the valid patterns.
%

%
%It is notable that, in star partition, original data is 
%replicated at most $O(|\mathbb{O}|)$ times.
%In later sections, we will describe several 
%more optimization techniques to further reduce the amount of replicated data.

@@

\eat{

@@

It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
reduces, thus the terminating power of $FC$ would be stronger. We give hybrid example of the three
optimization as follows:
%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
%all candidates. Then, the following \emph{forward closure checking} rule can be used:
%
%\begin{theorem}[Forward Closure Checking Rule]
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
%$FC_i$ forms a valid GCMP .
%\end{theorem}
}

\subsection{Put It Together}
With the star partition and the Apriori enumerator, we are ready to assemble the Star Partition and ApRiori Enumerator (SPARE). 
We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship. In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers. Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created. Then the Apriori algorithm enumerate the true patterns from the candidate patterns. The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}. Note that we do not need to create an actual aggregate graph. Instead, we only to emitted the directed edges (Line~\ref{code:spm-edge-direct}).

\begin{algorithm}
\caption{Star Partition and ApRiori Enumerator}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map phase---}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$(o_1 ,o_2) \in C \times C$}
	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet, if $o_1 < o_2$~\label{code:spm-edge-direct}
	\EndFor
\EndFor
\label{code:spm-map-end}

\State {---Reduce phase---}
\label{code:spm-reduce-start}
\ForAll{$\langle o, Sr_{o} \rangle$}
\State AprioriEnumerator($Sr_o$)
\EndFor
\label{code:spm-reduce-end}

\end{algorithmic}
\end{algorithm}

Our SPARE framework does not rely on the pattern parameters to determine the partition size,
which is more stable than TRMP. In addition, we observe that the patterns mined from each
reducer are unique. This property is stated as follows:
\begin{theorem}[Pattern Uniqueness of Star Partition]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \not\equiv p_j.O$.
\end{theorem}
\begin{proof}
We prove by contradiction. Suppose exists $p_i \in P_i$ and $p_j \in P_j$ s.t. $p_i.O \equiv p_j.O$.
Let $o_i$ (resp. $o_j$) be the object with smallest ID in $p_i.O$ (resp. $p_j.O$).
Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$,  which contradicts with
the assumption $p_i.O \not\equiv p_j.O$. 
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} confirms the superiority of SPARE to TRPM. In TRPM, a pattern
may be repeatedly discovered from different partitions, while in SPARE a pattern is only discovered once. This suggests that SPARE require less redundant works. We finally conclude this section with the following theorem:

\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
See Appendix XXXX.
\end{proof}

\eat{ \subsection{Correctness of SPARE}
We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship. In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers. Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created. Then the Apriori algorithm enumerate the true patterns from the candidate patterns. Meanwhile, the \emph{simplification}, \emph{monotonicity pruning} and \emph{forward closure checking} are applied to boost the enumeration process.
ADD THE DETAILS WHEN THE REDUCER RECEIVE THE STAR PARTITIONS. HOW THEY DERIVE THE FINAL RESULT PATTERNS.

@@

In the following, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
If $P$ is a valid pattern in original trajectories, 
let $s$ be the object with smallest ID in $P.O$. 
Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
It follows that all object $o \in P.O$ are in $Sr_s$. 
Furthermore, every timestamp in $P.T$ is included
in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$. This ensures the \emph{completeness}. For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$. This ensure the \emph{soundness}.
\end{proof}

@@

This lemma verifies the superiority of the SPARE framework over the TRPM framework.
}
